Attestable Expiration with Trusted Platform Modules

### 2016-05-18 paper.tex
Minor edits.

Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, but it can be difficult to know who to trust. Even though we may trust a party at a given time, it can be difficult to know who we can trust in the future and impossible to know who might be compromised or subpeonaed. In recent years, there have been an increasing number of cases where courts mandated that a given thid party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.

@@

In order to achieve this property, we leverage two areas of prior work on cryptographic proofs-of-work: Trusted Platform Modules (TPMs), and Ethereum smart contracts. TPMs allow one to ensure that code has been executed correctly and without modification, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.

>>>>

Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, but it can be difficult to know whom to trust. Even though we may trust a party at a given time, it can be difficult to know who we can trust in the future and impossible to know who might be compromised or subpeonaed. In recent years, there have been an increasing number of cases where courts mandated that a given third party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.

@@

In order to achieve this property, we leverage two areas of prior work: Trusted Platform Modules (TPMs), and Ethereum smart contracts. TPMs allow one to provable attest that a given piece of code has been executed without modification, along with its inputs and outputs, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.
